Supplementary Methods for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-11-20 Documents/supplementary_information.tex
Tweaks

@@

We developed a country-level continuous-time mathematical model that
divides people aged $15$\;y and older into non-overlapping HIV states.
We focus on this age group because it accounts for the vast majority
of global PLHIV \autocite{UNICEF}, 93\% in 2014; because
population-level HIV estimates and demographic data are typically only
estimated for ages $15$--$49$; and to capture the continuing burden of
infections in people ages $50$ and older.

Our model has 8 HIV states (Extended Data Fig.~\ref*{model_diag}):
susceptible to HIV infection ($S$ is the number of people
susceptible), vaccinated against HIV ($R$), acute HIV infection ($A$),
undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
($D$), treated without viral suppression ($T$), viral suppression
($V$), and having AIDS ($W$).  Viral suppression is defined as a viral
load of less than 1000 viral RNA copies per mL of blood.  Viral
suppression not only extends survival but also dramatically reduces
transmission
\autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
Simulations of our model project the number of people in each HIV
stratum from 2015 to 2035.

>>>>

% For Nature, no page numbers.
\pagestyle{empty}
\usepackage{etoolbox}
\apptocmd{\maketitle}{\thispagestyle{empty}}{}{}

@@

We developed a country-level continuous-time mathematical model that
divides people aged $15$\;y and older into non-overlapping HIV states.
We focused on this age group because it accounts for the vast majority
of global PLHIV \autocite{UNICEF}, 93\% in 2014; because
population-level HIV estimates and demographic data are typically only
estimated for ages $15$--$49$; and to capture the continuing burden of
infections in people ages $50$ and older.  Our model has 8 HIV states
(Extended Data Fig.~\ref*{model_diag}): susceptible to HIV infection
($S$ is the number of people susceptible), vaccinated against HIV
($R$), acute HIV infection ($A$), undiagnosed HIV infection ($U$),
diagnosed but untreated HIV infection ($D$), treated without viral
suppression ($T$), viral suppression ($V$), and having AIDS ($W$).
Viral suppression is defined as a viral load of less than 1000 viral
RNA copies per mL of blood.  Viral suppression not only extends
survival but also dramatically reduces transmission
\autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
Simulations of our model project the number of people in each HIV
stratum from 2015 to 2035.
